---
title       : bigqueryR
subtitle    : R package for BigQuery.
author      : Yutaka Koga
job         : GA360 MSC APAC
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : solarized_light      # 
widgets     : [bootstrap, quiz]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
ext_widgets: {rCharts: [libraries/morris, libraries/nvd3]}

--- 

## Setup  
```{r cache=FALSE, echo=FALSE}
library(knitr)
read_chunk('./bigqueryR-sample.R')
```
### Prerequisites  
1. [required] Install [R](https://www.r-project.org/) (recommended to user latest version.)  
2. [optional] Install [RStudio](https://www.rstudio.com/)  
  
### Install bigqueryR  
```
install.packages('bigqueryR')
```

---

## Initial instructions  
### Load bigqueryR 
```{r initial-setup, results='asis', cache=FALSE}
```

### Authentication  
```{r auth, results='asis', cache=FALSE}
```

### Get lists of your project and datasets  
```{r list-projects, results='asis', cache=FALSE, eval=FALSE}
```

--- 

## Query Analytics 360 data on BigQuery  
### Query pre-defined metrics and dimensions.  
```{r query1, results='asis', cache=FALSE, eval=FALSE}
```

---

## Query Analytics 360 data on BigQuery  
### Or you can query with an any custom query.  
```{r query2, results='asis', cache=FALSE, eval=FALSE}
```

---

## Visualize data  
### Now you can show chart with R functionality.  
```{r scatter-plot, results='asis', cache=FALSE}
```

---

## Visualize data  
### Time series as follows.  
```{r line-plot, results='asis', cache=FALSE}
```
